# Lists

A list in R can contain many different data types inside it. A list is a collection of data which is ordered and changeable.Unlike Vectors which only can accommodate a single data type,we can also say that vectors are Homogeneous and lists are heterogeneous.

To create a list, use the list() function:

```{r}
# List of strings
l <- list("A", "B", "C",1,2,3,"!","@")

# Print the list
l
```

Accessing lists.

```{r}
thislist <- list("X", "y", 1)
thislist[3]
```

To change the value of a specific item, refer to the index number:

```{r}
# x to b
thislist[1] <- "b"

# Print the updated list
thislist
```

Length of a list.

```{r}
length(thislist)
```

## Check if Item Exists

To find out if a specified item is present in a list, use the %in% operator:

```{r}
this <- list("apple", "banana", "cherry")

"apple" %in% this

```

To add an item to the end of the list, use the append() function:

```{r}
append(this, 1)
```

add more as a vector

```{r}
append(this,c(1,2,3))
```

To add an item to the right of a specified index, add "after=indexnumber" in the append() function:

```{r}
append(this, "!@#%^", after = 3)
```

Removing items from the list

```{r}
newlist <- this[-1]

# Print the new list
newlist
```

Range of Indexes

```{r}
this2 <- list("A", "B", "C", "D", "E", "F", "G")

(this2)[2:5]
```

Looping through a list using For Loop

```{r}
for (x in this2) {
  print(x)
}
```

Joining Two Lists

```{r}
list1 <- list("a", "b", "c")
list2 <- list(1,2,3)
list3 <- c(list1,list2)

list3
```
