# Logistic Regression

Logistic regression in R Programming is a classification algorithm used to find the probability of event success and event failure. Logistic regression is used when the dependent variable is binary(0/1, True/False, Yes/No) in nature. Logit function is used as a link function in a binomial distribution.

```{r}
#mtcars is an inbuit dataset in R (Motor Trend Car Road Tests))

# Installing the package
install.packages("caTools")    # For Logistic regression
install.packages("ROCR")       # For ROC curve to evaluate model
```

Loading the packages

```{r}
library(caTools)
library(ROCR) 

```

### Splitting dataset

```{r}
split <- sample.split(mtcars, SplitRatio = 0.8)
split
```

```{r}
train_reg <- subset(mtcars, split == "TRUE")
test_reg <- subset(mtcars, split == "FALSE")
# glm(response ~ predictor, family = binomial(link = "logit"), data) 

```

### Training model

```{r}
logistic_model <- glm(vs ~ wt + disp, 
                      data = train_reg, 
                      family = "binomial")
logistic_model

# Summary
summary(logistic_model)

```

Predict test data based on model

```{r}
predict_reg <- predict(logistic_model, 
                       test_reg, type = "response")
predict_reg  
```

Changing probabilities

```{r}
predict_reg <- ifelse(predict_reg >0.5, 1, 0)
```

### Evaluating model accuracy using confusion matrix

```{r}
table(test_reg$vs, predict_reg)

missing_classerr <- mean(predict_reg != test_reg$vs)
print(paste('Accuracy =', 1 - missing_classerr))
```

ROC-AUC Curve

```{r}
ROCPred <- prediction(predict_reg, test_reg$vs) 
ROCPer <- performance(ROCPred, measure = "tpr", 
                      x.measure = "fpr")

auc <- performance(ROCPred, measure = "auc")
auc <- auc@y.values[[1]]
auc
```

### Plotting curve

```{r}
plot(ROCPer)
plot(ROCPer, colorize = TRUE, 
     print.cutoffs.at = seq(0.1, by = 0.1), 
     main = "ROC CURVE")
abline(a = 0, b = 1)

auc <- round(auc, 4)
legend(.6, .4, auc, title = "AUC", cex = 1)
```

### 
