# Vectors

Here the Vectorization of numerical Values are Done.

```{r}
# Vector of numerical values
numbers <- c(1, 2, 3)

# Print numbers
numbers
```

Vectorization of String datatype.

```{r}
#Vector in String values.
xx<-c("A","B","C")

xx

```

Vectorization in a Sequence.

```{r}
# Vector with numerical values in a sequence
numbers <- 1:10

numbers
```

Vectors with Numerical sequence

```{r}
# Vector with numerical decimals in a sequence
numbers1 <- 12.33:6.33
numbers1

# Vector with numerical decimals in a sequence where the last element is not used
numbers2 <- 1.5:6.3
numbers2
```

Vectors and Logical values(T/F)

```{r}
# Vector of logical values
log_values <- c(TRUE, FALSE, TRUE, FALSE)

log_values
```

Vector length /length() fn

```{r}
fruits <- c("mango", "apple", "pear")

length(fruits)
```

To sort items in a vector alphabetically or numerically, use the sort() function :

```{r}
xv <- c("X", "XX", "XXX", "XXXX", "XXXXX")
numbers <- c(13, 3, 5, 7, 20, 2)

sort(xv)  # Sort a string
sort(fruits)
sort(numbers) # Sort numbers

```

Accessing Vectors

```{r}
A <- c("AB", "CD", "EF")

# Access the first item (banana)
A[1]
A[3]
```

You can also access multiple elements by referring to different index positions with the c() function:

```{r}
animals <-c("Cat","Dog","Horse","Monkey","Cow","Bull","Giraffee","Zebra")

# Access the first and third item (cat and horse).
animals[c(1, 3)]
```

You can also use negative index numbers to access all items except the ones specified:

```{r}
# Access all items except for the first item.
#Unlike Pyton there is no backward indexing here "-" means without.
animals[c(-1)]
```

To change the value of a specific item, refer to the index number:

```{r}
#First acces the element and then alter the vlaue.
#(cat to Siberian Husky).
animals[c(1)]<-"Siberian Husky"  
animals
```

To repeat vectors, use the rep() function:

```{r}
#feed in an array.
#Use the Rep(),and give parameters,ie values and how many times to repeat(each).
arr <-c(1,2,3)
repeat_each <- rep(arr, each = 3)
repeat_each
```

for Repeating a sequence

```{r}
repeat_times <- rep(c(1,2,3), times = 3)

repeat_times

```

Now to repeat each value independently

```{r}
#Just like repeating but this time 
repeat_indepent <- rep(c(1,2,3), times = c(5,2,1))

repeat_indepent
```

Generation of sequenced Vectors

```{r}
num <- 1:10

num
```

To make bigger or smaller steps in a sequence, use the seq() function:

```{r}
n <- seq(from = 0, to = 100, by = 20)

n

```
